\hspace{1cm} Do syntactic and semantic similarity lead to interference effects? \newline Evidence from self-paced reading and event-related potentials using German

### 2024-08-28 paper/main.tex
minor wording change

\subsection{\textcolor{blue}{Comparison with previous findings}}\label{comparison}
\Copy{comparison}{\textcolor{blue}{The present study used the same design as two previous studies \parencite{vandyke07, mertzen}. Figure \ref{fig:previous_vs_present} A shows the estimated reading times differences from the previous studies and the present self-paced reading experiment. Because the \textcite{vandyke07} data was not available to us, we derived estimates for their study from the summary statistics in the published paper. \textcite{mertzen} made their data available. In comparison to the previous estimates, the effects of the present study are relatively small and associated with less uncertainty in general. The present and previous estimates of semantic interference seem relatively consistent: They indicate a positive effect which is largest in the pre-critical region and smallest in the critical region. It seems like the present estimates of syntactic interference are smaller, i.e., closer to zero, than the previous estimates. For the interaction, the present estimates are larger, i.e., further from zero in the positive direction, than the previous ones. To see whether there is evidence for the estimated effects, we computed Bayes factors for the previous studies to compare them to the present Bayes factors. For maximal comparability, we used only the self-paced reading times and total fixation times from the previous studies for this comparison. To compute Bayes factors for \textcite{vandyke07}, we used the Normal-Normal conjugate case to derive posteriors from the summary statistics (mean and SE) in the published paper. Then, using these posteriors and a reasonable prior (Normal(0,0.5), a priori assumed effect size in the range of -40 ms to 40 ms), we computed Bayes factors with the Savage-Dickey method. Bayes factors for \citeauthor{mertzen}'s (\citeyear{mertzen}) data were computed using the Savage-Dickey method from hierarchical mixed models which we ran on their data analogously to our own analyses described in Statistical Analyses for Experiments 1a and b. The Bayes factors for the effects of interest of the present and previous studies under prior Normal(0,0.5) are shown in Figure \ref{fig:previous_vs_present} B.}

>>>>

\subsection{\textcolor{blue}{Comparison with previous findings}}\label{comparison}
\Copy{comparison}{\textcolor{blue}{The present study used the same design as two previous studies \parencite{vandyke07, mertzen}. Figure \ref{fig:previous_vs_present} A shows the estimated reading times differences from the previous studies and the present self-paced reading experiment. Because the \textcite{vandyke07} data was not available to us, we derived estimates for their study from the summary statistics in the published paper. \textcite{mertzen} made their data available. In comparison to the previous estimates, the effects of the present study are relatively small and associated with less uncertainty in general. The present and previous estimates of semantic interference seem relatively consistent: They indicate a positive effect which is largest in the pre-critical region and smallest in the critical region. It seems like the present estimates of syntactic interference are smaller, i.e., closer to zero, than the previous estimates. For the interaction, the present estimates are larger, i.e., further from zero in the positive direction, than the previous ones. To see whether there is evidence for the estimated effects, we computed Bayes factors for the previous studies to compare them to the present Bayes factors. For maximal comparability, we used only the self-paced reading times and total fixation times from the previous studies for this comparison. To compute Bayes factors for \textcite{vandyke07}, we used the Normal-Normal conjugate case to derive posteriors from the summary statistics (mean and SE) in the published paper. Then, using these posteriors and a reasonable prior (Normal(0,0.5), which amounts to an a priori assumed effect size in the range of -40 ms to 40 ms), we computed Bayes factors with the Savage-Dickey method. Bayes factors for \citeauthor{mertzen}'s (\citeyear{mertzen}) data were computed using the Savage-Dickey method from hierarchical mixed models which we ran on their data analogously to our own analyses described in Statistical Analyses for Experiments 1a and b. The Bayes factors for the effects of interest of the present and previous studies under prior Normal(0,0.5) are shown in Figure \ref{fig:previous_vs_present} B.}
